### 2014-12-18 sharp-sigma-one-plus.tex

We define the vocabulary $\L = \{ P_1, ..., P_r, S_1,...,S_t, \leq \}$, where $P_1, ..., P_r$ have arity $a_1,...,a_r$, and $S_1,...,S_t$ have arity $b_1,...,b_t$. Let $\L\prime = \{ S_1,...,S_t, \leq \}$, and let
\begin{eqnarray*}
\textsc{Struct[\L]} &=& \{\A \mid \A \text{ is an } \L\prime \text{-structure with a finite domain } A \text{ such that} \\
&& \leq \text{ is interpreted as a total order for } A \}.
\end{eqnarray*}
A quantifier-free $\L$-formula is defined by the following grammar:
\begin{eqnarray*}
\varphi &::=& x = y \mid S_i(x_1,...,x_{b_i}), i \in \{1,...,t\} \mid x \leq y \mid \\
&& P_i(x_1,...,x_{a_i}), i \in \{1,...,r\} \mid \\ 
&& (\neg \varphi) \mid (\varphi \wedge \varphi) \mid (\varphi \vee \varphi),
\end{eqnarray*}
where $x, y$ are variables. We now define a quantifier-free$^{+}$ $\L$-formula as such:
\begin{eqnarray*}
\varphi &::=& \alpha, \alpha \text{ is a FO-formula over } \L\prime  \mid \\
&& P_i(x_1,...,x_{a_i}), i \in \{1,...,r\} \mid \\
&& (\neg \varphi) \mid (\varphi \wedge \varphi) \mid (\varphi \vee \varphi).
\end{eqnarray*}
Let $\P = (P_1, ..., P_r)$ and $\S = (S_1,...,S_t)$. A function $\F:\textsc{Struct[\L]} \to \mathbb{N}$ is in $\#\Sigma_1^+$ if there exists a quantifier-free$^{+}$ $\L$-formula $\varphi(\x,\P,\z)$ such that
\begin{eqnarray*}
\F &=& \mid \{ \langle \P, \z \rangle \mid \A \models \exists \x \: \varphi(\x,\P,\z) \} \mid
\end{eqnarray*}
for every $\A \in \textsc{Struct[\L]}$. We refer to predicates in $\P$ and variables in $\z$ as ``open", and predicates in $\S$ and variables in $\x$ as ``closed".

>>>>

We define the vocabulary $\L = \{ P_1, ..., P_r, S_1,...,S_t, \leq \}$, where $P_1, ..., P_r$ have arity $a_1,...,a_r$, and $S_1,...,S_t$ have arity $b_1,...,b_t$. Let $\L\prime = \{ S_1,...,S_t, \leq \}$, and let
\begin{eqnarray*}
\textsc{Struct}[\L] &=& \{\A \mid \A \text{ is an } \L\prime \text{-structure with a finite domain } A \text{ such that} \\
&& \leq \text{ is interpreted as a total order for } A \}.
\end{eqnarray*}
A quantifier-free $\L$-formula is defined by the following grammar:
\begin{eqnarray*}
\varphi &::=& x = y \mid S_i(x_1,...,x_{b_i}), i \in \{1,...,t\} \mid x \leq y \mid \\
&& P_i(x_1,...,x_{a_i}), i \in \{1,...,r\} \mid \\ 
&& (\neg \varphi) \mid (\varphi \wedge \varphi) \mid (\varphi \vee \varphi),
\end{eqnarray*}
where $x, y$ are variables. We now define a quantifier-free$^{+}$ $\L$-formula as such:
\begin{eqnarray*}
\varphi &::=& \alpha, \alpha \text{ is a FO-formula over } \L\prime  \mid \\
&& P_i(x_1,...,x_{a_i}), i \in \{1,...,r\} \mid \\
&& (\neg \varphi) \mid (\varphi \wedge \varphi) \mid (\varphi \vee \varphi).
\end{eqnarray*}
Let $\P = (P_1, ..., P_r)$ and $\S = (S_1,...,S_t)$. A function $\F:\textsc{Struct[\L]} \to \mathbb{N}$ is in $\#\Sigma_1^+$ if there exists a quantifier-free$^{+}$ $\L$-formula $\varphi(\x,\P,\z)$ such that
\begin{eqnarray*}
\F &=& \mid \{ \langle \P, \z \rangle \mid \A \models \exists \x \: \varphi(\x,\P,\z) \} \mid
\end{eqnarray*}
for every $\A \in \textsc{Struct[\L]}$. We refer to predicates in $\P$ and variables in $\z$ as ``open", and predicates in $\S$ and variables in $\x$ as ``closed".
